Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-08-16 peakcharacterization_manuscript.Rmd
starting the section on changes to RSD, b/c this is *really* the biggest point of the whole paper demonstrating that the characterization as a whole has an effect

>>>>

### Changes in RSD

Each step in the peak characterization either changes the overall number of peaks coming from each scan (sliding windows and breaking initial regions) or the overall intensity of the points within a scan. Therefore, one way to quantify any potential *improvements* in the characterized peaks is to look at the relative standard deviation for the characterized scan level peak intensities, and compare them as each processing step is introduced.
